Developing a preprint culture in biology

### 2012-10-01 ms.tex
add support KR
Tim modifs

Furthermore, the review process as a whole is critically over-loaded, because as
the number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the reviewers
commons'' REF.  At the same time, rejection rates are high in most journals
(REF), and when not invited to submit a revision, authors must start the whole
process all over again.  Initiatives to reduce time from submission to
publication have emerged across the scientific community XXX et coll.  (REF)
called for the recycling and reuse of peer-reviews: by attaching previous
reviews and detailed replies to a new submission, both the editor and the
referees can gauge the work done on the manuscript, and perhaps evaluate it with
less prejudice. In a similar way, the \emph{Peerage of Science} initiative
allows authors to seek anonymous pre-review by their peers. Some journals now
accept to publish papers which received good evaluations, with \emph{Animal
Biology} having recently accepted first a paper reviewed entirely with the
\emph{Peerage of Science} \cite{abb12}, effectively outsourcing the review
process. A widespread use of preprint servers can achieve the same goal of
reducing the time spent in review. By putting a manuscript for open comments and
criticisms, the authors will receive valuable feedback and can improve the
version which will be submitted. With a rich enough community of scientists
depositing preprints, and commenting on them, the process of an open pre-review
can become widespread and will overall increase the quality of first
submissions.

@@

F1000Research is not a public preprint server like the previous three servers.
Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
without having it reviewed, papers submitted to F1000Research will eventually be
reviewed. Thus, F1000Research offers a hybrid model with publicly available
manuscripts at time of submission and standard peer-reviews. Manuscripts are
considered ``accepted'' and will only be indexed after two positive referee
response.

@@

This manuscript was developed entirely as an open project on github. github is
one of several hosting services for collaborative development using the git
revision control software.  git is a decentralized revision control system
created by Linus Torvalds and is used primarily to develop software, including
the Linux kernel. It allows the users to share code, track changes, and merge
versions. For example, during the development of this manuscript, one author
would fork the project (i.e.: make a personal copy), modify it, and then the
changes were merged back into the main branch. These techniques are widely used
in open source software development. It goes even farther than submitting
preprints by opening the entire writing process.

>>>>

Furthermore, the review process as a whole is critically over-loaded, because
as the number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the reviewers
commons'' REF.  At the same time, rejection rates are high in most journals
(REF), and when not invited to submit a revision, authors must start the whole
process all over again.  Initiatives to reduce time from submission to
publication have emerged across the scientific community. XXX et coll.  (TREE
paper recylce, reuse, ...) called for the recycling and reuse of peer-reviews:
by attaching previous reviews and detailed replies to a new submission, both
the editor and the referees can gauge the work done on the manuscript, and
perhaps evaluate it with less prejudice. In a similar way, the \emph{Peerage
of Science} initiative allows authors to seek anonymous pre-review by their
peers. Some journals now accept to publish papers which received good
evaluations, with \emph{Animal Biology} having recently accepted first a paper
reviewed entirely with the \emph{Peerage of Science} \cite{abb12}, effectively
outsourcing the review process. A widespread use of preprint servers can
achieve the same goal of reducing the time spent in review. By putting a
manuscript for open comments and criticisms, the authors will receive valuable
feedback and can improve the version which will be submitted. With a rich
enough community of scientists depositing preprints, and commenting on them,
the process of an open pre- review can become widespread and will overall
increase the quality of first submissions.

@@

F1000Research is not a public preprint server like the previous three servers.
Whereas arXiv, Figshare, and PeerJ offer an option to submit a manuscript
without having it reviewed, papers submitted to F1000Research will eventually
be reviewed. Thus, F1000Research offers a hybrid model with publicly available
manuscripts at time of submission and standard peer-reviews. Manuscripts are
considered ``accepted'' and will only be indexed after two positive referee
response. F1000Research works closely with data providers to integrate raw
data to the paper. Forinstance, upon submitting a paper, authors are asked to
upload their data, which are then integrated in \emph{e.g.} FigShare widgets,
the DOI of which are given in the paper when the data are first mentionned.
The licensing of the data is similar to the one used by FigShare, meaning that
the articles are free to access, and can be redistributed readily. By putting
much effort in integrating data to the paper, F1000Research is working to make
science more reproducible and open.

@@

This manuscript was developed entirely as an open project on github. github is
one of several hosting services for collaborative development using the git
revision control software.  git is a decentralized revision control system
created by Linus Torvalds and is used primarily to develop software, including
the Linux kernel. It allows the users to share code, track changes, and merge
versions. For example, during the development of this manuscript, one author
would fork the project (\emph{i.e.} make a personal copy), modify it, and then the
changes were merged back into the main branch. These techniques are widely used
in open source software development. It goes even farther than submitting
preprints by opening the entire writing process.
